Flabby and injective objects in toposes

### 2022-02-16 paper-flabby-objects.tex
typo (thanks to Lukas Stoll)

As a byproduct, we demonstrate how the notion of flabby sets is a useful
organizing principle in the study of injective objects. We employ flabby sets
to give a new proof of Roswitha Harting's results that injectivity of sheaves is
a local notion~\cite{harting:remark} and that a sheaf is injective if and only
if it is injective from the internal point of
view~\cite{harting:locally-injective}, which she stated (in slightly different
language) for sheaves of abelian groups. We use the opportunity to correct a
small mistake of hers, namely claiming that the analogous results for sheaves of
modules would be false.

@@

\textbf{Acknowledgments.} We are grateful to Thorsten Altenkirch, Simon Henry
and Maria Emilia Maietti for insightful discussions and pointers to prior work,
to Jürgen Jost, Marc Nieper-Wißkirchen and Peter Schuster for valuable
guidance, and to Daniel Albert and Caterina Cozzi for their careful readings of
earlier drafts. The work for this note was carried out at the University of
Augsburg, the Max Planck Institute for Mathematics in the Sciences in
Leipzig and the University of Verona.

@@

% Take care: This paragraph is referenced in prop:global-elements.
If~$F$ is a flabby sheaf in the traditional sense, then~$F$ is obviously also
flabby in the sense of Definition~\ref{defn:flabby-sheaf} -- singleton
coverings will do. Conversely, let~$F$ be a flabby sheaf in the sense of
Definition~\ref{defn:flabby-sheaf}. Let~$s \in F(U)$ be a local section. Zorn's
lemma implies that there is a maximal extension~$s' \in F(U')$. By assumption,
there is an open covering~$X = \bigcup_i U_i$ such that, for all~$i$, the
section~$s'$ can be extended to~$U' \cup U_i$. Since~$s'$ is maximal, $U' \cup
U_i = U'$ for all~$i$. Therefore~$X = \bigcup_i U_i \subseteq U'$; hence~$s'$ is a
global section, as desired.

>>>>

As a byproduct, we demonstrate how the notion of flabby sets is a useful
organizing principle in the study of injective objects. We employ flabby sets
to give a new proof of Roswitha Harting's results that injectivity of sheaves is
a local notion~\cite{harting:remark} and that a sheaf is injective if and only
if it is injective from the internal point of
view~\cite{harting:locally-injective}, which she stated (in slightly different
language) for sheaves of abelian groups. We use the opportunity to correct a
small inaccuracy of hers, namely claiming that the analogous results for sheaves of
modules would be false.

@@

\textbf{Acknowledgments.} We are grateful to Thorsten Altenkirch, Simon Henry
and Maria Emilia Maietti for insightful discussions and pointers to prior work,
to Jürgen Jost, Marc Nieper-Wißkirchen and Peter Schuster for valuable
guidance, and to Daniel Albert and Giacomo Cozzi for their careful readings of
earlier drafts. The work for this note was carried out at the University of
Augsburg, the Max Planck Institute for Mathematics in the Sciences in
Leipzig and the University of Verona.

@@

% Take care: This paragraph is referenced in prop:global-elements.
If~$F$ is a flabby sheaf in the traditional sense, then~$F$ is obviously also
flabby in the sense of Definition~\ref{defn:flabby-sheaf} -- the singleton
covering~$X = X$ will do. Conversely, let~$F$ be a flabby sheaf in the sense of
Definition~\ref{defn:flabby-sheaf}. Let~$s \in F(U)$ be a local section. Zorn's
lemma implies that there is a maximal extension~$s' \in F(U')$. By assumption,
there is an open covering~$X = \bigcup_i U_i$ such that, for all~$i$, the
section~$s'$ can be extended to~$U' \cup U_i$. Since~$s'$ is maximal, $U' \cup
U_i = U'$ for all~$i$. Therefore~$X = \bigcup_i U_i \subseteq U'$; hence~$s'$ is a
global section, as desired.
